Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-20 manuscript/manuscript.tex
Figures names changed in manuscript

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dlinear-thin-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dlinear-thick-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-shifted-thin-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-shifted-thick-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences-thin.pdf}
\caption{
    Results of the accuracy tests for different exponential density functions in case of a spherical shell of 1km of thickness.
    (a) Density functions used in the tests, each one with a different value of $b$ and normalised in such way that they reaches a density of 2900kg/m$^{3}$ at the bottom of the shell.
    (b) Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for each density function. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power-thin}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Ddiscontinuous-symmetric-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the discontinuous density defined on equation \ref{eq:density-discontinuous} and $R_c$ as the centre radius of the shell. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-discont-sym}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Ddiscontinuous-asymmetric-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the discontinuous density defined on equation \ref{eq:density-discontinuous} and $R_c=(R_1 + R_2)/3$. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-discont-asym}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/linear-D-thin.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/linear-D-thick.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-D-thin.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-D-thick.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness with the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thick}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/exponential-b-thin.pdf}
\caption{
    Results of the accuracy tests for different exponential density functions in case of a spherical shell of 1km of thickness.
    (a) Density functions used in the tests, each one with a different value of $b$ and normalised in such way that they reaches a density of 2900kg/m$^{3}$ at the bottom of the shell.
    (b) Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for each density function. Each computation was performed on the big grid described in Table \ref{tab:grids}, for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power-thin}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/discontinuous-D-sym.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the discontinuous density defined on equation \ref{eq:density-discontinuous} and $R_c$ as the centre radius of the shell. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-discont-sym}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/discontinuous-D-asym.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness with the discontinuous density defined on equation \ref{eq:density-discontinuous} and $R_c=(R_1 + R_2)/3$. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 0.1\%, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-discont-asym}
\end{figure}
